\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-09-30 paper2015asml.tex
modifying procedure

\title{\LARGE \bf
WORKING TITLE: Incorporating User Feedback in Motion Planning for Manipulators
}

@@

\section{Approach}
\label{sec:survey}
Our approach starts with an online survey designed to get information from multiple users about how well they like robot trajectories. In this section, we will describe in detail the infrastructure used to create the trajectories and movies that were used in the survey and the online 
survey procedure used.

\subsection{System Infrastructure}

In order to quickly produce a large number of robot trajectories, the MoveIt benchmarking architecture~\cite{cohen2012generic} was extended with video recording capabilities. Every trajectory was generated by a combination of \emph{scenes}, \emph{queries}, and \emph{planners}. In this paper, our trajectories are planned in three distinct scenes (shown in~\ref{fig:scenes}) which the robot can interact in: a kitchen (\emph{Countertop}), an industrial workbench (\emph{Industrial}) and a drawer on a table (\emph{Drawer}).

@@

After selecting the scenes, the robot was positioned in the scenes manually and planning queries were constructed by hand to reach a requisite number of planned trajectories~\ref{fig:design}. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

Finally, the planning algorithms that were used were RRT-Connect~\cite{kuffner2000rrt}, and RRT*~\cite{frazzoli-RRTstar} with two cost functions: \emph{PathLength} and \emph{MaxMinClearance}.The objective for \emph{PathLength} minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for \emph{MaxMinClearance} computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize.

\todo cite OMPL and optimal planning

@@

The library of trajectory videos was collected by computing plans with each of the previously discussed planners for the planning queries and scenes hand-picked from above. The plans were then recorded in simulation through RVIZ. In designing the online survey, these video recordings would be taken from multiple vantage points to maximize the visibility of the motion to the participant reviewing it.

\subsection{Online Survey}

\begin{figure}
    \frame{\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_survey_screenshot}}
    \caption{The main survey question which prompts the participant for a rating in four motion characteristics (efficiency, elegance, smoothness and overall impression) after presenting a video that demonstrates the motion from four clearly visible vantage points for any sample trajectory.}
    \label{fig:survey_question}
\end{figure}

Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once.The analysis of these results will be done in Section~\ref{sec:analysis}.

>>>>

\title{\LARGE \bf
Towards a Data-driven Approach to Motion Planning
}

@@

\section{Approach}
\label{sec:survey}
Our approach starts with an online survey designed to get information from multiple users about how well they like robot trajectories. In this section, we will describe in detail the infrastructure used to create the trajectories and movies that were used in the survey. We will also describe the online survey procedure in detail.

\subsection{Planning System Infrastructure}

The MoveIt! benchmarking architecture~\cite{cohen2012generic} was extended with video recording capabilities to quickly generate a large number of trajectories. The MoveIt! architecture allows for the definition of environments, referred to as planning scenes, start and goal states for robots (motion planning queries). It also allows for the use of any supported planning algorithms (planners). A combination of different scenes, motion queries, and planners was used to generate robot trajectories for evalutation. We chose three distinct scenes (shown in~\ref{fig:scenes}): a kitchen ({\sc Countertop}), an industrial workbench ({\sc Industrial}) and a drawer on a table ({\sc Drawer}). Multiple queries were generated in each scene for motions of the right arm of the PR2 robot. The robot was positioned in the scenes manually and motion planning queries were constructed by hand~\ref{fig:design}. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

@@

The planning algorithms that were used were RRT-Connect~\cite{kuffner2000rrt} and RRT*.  RRT*~\cite{frazzoli-RRTstar} was used with two different cost functions: \sc{PathLength} and \sc{MaxMinClearance}.The objective for \sc{PathLength} minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for \sc{MaxMinClearance} computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize. Both planners are implemented in the OMPL library~\ref{OMPL:2012}.

@@

The infrastructure we designed around MoveIt! allowed us to automatically generate movies of the generated trajectories using the ROS Visualizer (Rviz). We generated movies from different viewpoints to maximize the visibility of the motion to human observers reviewing it. Each participant was allowed to provide feedback no more than once for each of the trajectories generated by the survey design. We ran the survey for 103 trajectories, requesting no more than 20 ratings per trajectory. Participants are allowed to rate multiple distinct trajectories, but no more than once. The analysis of these results is presented in Section~\ref{sec:analysis}.

\subsection{Online Survey}
\begin{figure}
    \frame{\includegraphics[trim = 0mm 0mm 0mm 0mm, width=\columnwidth]{pictures/amazon_survey_screenshot}}
    \caption{The main survey question which prompts the participant for a rating in four motion characteristics (efficiency, elegance, smoothness and overall impression) after presenting a video that demonstrates the motion from four clearly visible vantage points for any sample trajectory.}
    \label{fig:survey_question}
\end{figure}
